Co-citations in context

### 2019-09-11 cocit_r_v2.tex
resetting revisions

\begin{itemize}
\item Conventionality and Innovativeness are part of the framework developed by Uzzi. We neither challenge nor embrace the framework but simply use it a read out. The reviewer is holding us responsible for Uzzi's construct.
\item We provide quantitative data addressing the reference count issue.
\end{itemize}

@@

An irresponsible choice of words- `I do not think this paper can get away with it...' We are not trying to get away with anything!  Perhaps the reviewer confuses her/his own clumsy sophistry with our presentation? If so, it is most regrettable and we will strive to  ensure a distinction. Secondly, the reviewer's critique suffers from being somewhat incoherent. Even so....
\begin{itemize}
\item An illustration has been provided
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not
\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons
\end{itemize}

>>>>

\begin{itemize}
\item This is an interesting point. We reviewed the literature in which correlation between reference count and citations is asserted. 
\item We provide quantitative data addressing the reference count issue and conclude that the relationship is not a strong one...
\end{itemize}

@@

\begin{itemize}
\item An illustration has been provided
\item Yes, a difference between bibliometrics and mathematics may be that bibliometrics papers cite mathematics papers more often than the other way around. The local model accounts for this but the global one does not
\item The relationship between novelty and conventionality is not a ground truth, we have never claimed it is. This framework was developed by Uzzi et al. (2013) and we have used it to enable \emph{ceteris paribus} comparisons
\end{itemize}

\subsection{Editor}
\emph{I have one other suggestion. In addition to the work on novelty by Brian Uzzi and colleagues, there is also work on novelty by Reinhilde Veugelers and colleagues, who operationalize novelty in a different way. For completeness, you may consider providing a brief discussion of the work by Veugelers and colleagues in your manuscript.}
\begin{itemize}
\item We thank you for bringing this to our attention. Discussing this paper broadens the scope of our manuscript and we've referenced it in the Discussion. As one of our co-authors pointed out, the definition of novelty is a little restrictive to say the least but the rest of the paper is excellent.
\end{itemize}
